Conference Paper Title*\\ {\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and should not be used} \thanks{Identify applicable funding agency here. If none, delete this.}

### 2024-03-10 paper/paper.tex
adapted half of class paper to latex

\begin{IEEEkeywords}
component, formatting, style, styling, insert
\end{IEEEkeywords}

\section{Introduction}
Inspired by the recent advent of graphical neural networks (GNNs), this project explores their potential to classify academic networks. Given any individual publication or author, GNNs could predict their relation to the remainder of the network, useful for understanding the relationships between academic fields, authors, institutions, and more. This opens the door to opportunities for classifying papers in fields with minimal representation in existing citation networks or predicting links between papers, potentially applicable to discovering inspiring papers related to an author's past work,  among other capabilities. \par
In particular, machine learning hardware is a new field that has skyrocketed from the recent popularity of machine learning. Due to the compute-intensive nature of this field, plenty of research exists in the hardware infrastructure to support these computing loads. We utilize GNNs for node classification and link prediction to explore existing datasets and comment on the new corpus of machine learning hardware papers. The main challenges are processing data for useful representations of the network and data interpretation on the created GNNs to comment on the field of machine learning hardware. \par
\section{Ease of Use}

\subsection{Maintaining the Integrity of the Specifications}

The IEEEtran class file is used to format your paper and style the text. All margins, 
column widths, line spaces, and text fonts are prescribed; please do not 
alter them. You may note peculiarities. For example, the head margin
measures proportionately more than is customary. This measurement 
and others are deliberate, using specifications that anticipate your paper 
as one part of the entire proceedings, and not as an independent document. 
Please do not revise any of the current designations.

\section{Prepare Your Paper Before Styling}
Before you begin to format your paper, first write and save the content as a 
separate text file. Complete all content and organizational editing before 
formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on 
proofreading, spelling and grammar.

>>>>

% \begin{IEEEkeywords}
% component, formatting, style, styling, insert
% \end{IEEEkeywords}

\section{Introduction and Motivation}
Inspired by the recent advent of graphical neural networks (GNNs), this project explores their potential to classify academic networks. 
Given any individual publication or author, GNNs could predict their relation to the remainder of the network, 
useful for understanding the relationships between academic fields, authors, institutions, and more. This opens the door to 
opportunities for classifying papers in fields with minimal representation in existing citation networks or predicting links 
between papers, potentially applicable to discovering inspiring papers related to an author's past work, 
among other capabilities. \par

In particular, machine learning hardware is a new field that has skyrocketed from the recent popularity of machine learning. 
Due to the compute-intensive nature of this field, plenty of research exists in the hardware infrastructure to support these 
computing loads. We utilize GNNs for node classification and link prediction to explore existing datasets and comment on the 
new corpus of machine learning hardware papers. The main challenges are processing data for useful representations of the network 
and data interpretation on the created GNNs to comment on the field of machine learning hardware. \par
\section{Previous Work}
There have been many previous explorations of citation networks using the datasets Cora, Citeseer, and PubMed Diabetes. 
In these citation networks, in particular, node classification and link prediction have been heavily explored. 
In Optimization of Graph Neural Networks with Natural Gradient Descent, Izadi et al improve on traditional optimization 
algorithms such as ADAM and stochastic gradient descent (SGD), producing a superior accuracy (90.16±0.59\%) 
by utilizing a proposed method inspired by natural gradient descent [1]. This paper achieved the highest accuracy across 
71 different papers done on node classification of the Cora dataset.  \par

Those that explored link prediction in the Cora and Citeseer datasets have achieved great results as well. 
In ‘NESS: Node Embeddings from Static SubGraphs,’ Ucar proposed splitting up the graph into multiple subgraphs 
that do not have overlapping edges in between subgraphs, using each graph to train and obtain node representations, 
then aggregating the results to obtain predictions [2]. Using this, he was able to obtain state-of-the-art accuracy results, 
achieving 98.94±0.1\% on Citeseer and 96.81±0.6\% on Cora. In ‘Neural Link Prediction with Walk Pooling,’ L. 
Pan et al proposed a GNN architecture that adds attention mechanisms to GNNs, achieving an accuracy of 89.59±1.58\% [3]. 
These past studies show the efficacy of GNNs on academic publications for node classification and link prediction, and, 
since these accuracies were certainly impressive, we hope to use these networks as a baseline to examine the key features 
of different datasets and extract information to create a similar dataset about the subject of machine learning hardware.  \par

\section{Approach}

Two preconstructed datasets, Cora and CiteSeer, are large datasets of scientific machine learning papers. 
Each dataset contains papers from before 2008, with citations to other papers in the database as well as the 
vocabulary used. The nodes of the graph are the papers themselves, with topics and vocabulary as individual features, 
while the directed links are citations to other papers. Cora classifies each publication into one of seven categories: 
Theory, Reinforcement Learning, Genetic Algorithms, Neural Networks, Probabilistic Methods, Case Based, and Rule Learning. 
On the other hand, Citeseer classifies each publication into one of six categories: Agents, Artificial Intelligence, Database, 
Human Computer Interaction, Machine Learning, and Information Retrieval. \par

Meanwhile, PubMed is a database of diabetes publications that is classified into one of three classes [4]. As such, this 
dataset is similar to both Cora and CiteSeer, though it further explores the efficacy of GNNs on datasets outside of 
machine learning. This performance of this dataset can further validate parameters potentially affecting accuracies, 
such as edge count, classes, or path length,  in addition to explaining differences in different fields of publications. \par

Web of Science (WoS) is an online database of publication citations and information [5]. 
This online database created by Clarivate can be queried by genre and shows identifying information such as titles, 
references, and specific citations. As such, we can utilize the WoS dataset to address the goal of exploring additional 
datasets in machine learning hardware. Specifically, by downloading papers by (exclusive) topic, 
we can create a dataset representative of the field of machine learning and compare the performance of our dataset 
against GNNs alongside other common datasets to analyze its efficacy on these models and its viability as a dataset 
in an academic setting. Using this popular database, we query their dataset of publications for four categories: 
Machine Learning on the Edge, Neuromorphic Computing, Spiking Neural Networks, and Machine Learning Accelerator. 
In using the Web of Science database, we assume that the papers are representative of their assigned class and 
distinct from related classes. In this regard, the dataset that we curate is unique from other citation networks 
in that it will hold distinct characteristics and be of machine learning hardware, providing insight into the 
structure and nature of the machine learning hardware citation network. \par

Beginning with the provided models like Deep Graph Library, we take inspiration from existing methods, 
such as preprocessing methods discussed by the Semantic Scholar Academic Graph [6]. By constructing our 
datasets of publications, we will examine model characteristics of varying types of publication networks. 
We also explored other datasets to improve the diversity of our datasets. The  Microsoft Open Academic Graph [7], 
a large academic graph dataset, shows a promising example of dataset scale, though it has differences in 
features, scaling, and overlapping that can interfere with providing information about any one academic field. 
Here, the data set uses a variety of data types for the nodes, like publications, authors, and venues, with 
the links between each denoting a correlation. \par

Following the specified approach to our project goals, the main tasks of our project are as follows. 
First, we will apply the necessary pre-processing techniques to each dataset for model compatibility. 
Then, we will create a GNN model using each dataset that accurately predicts paper topics and citations, 
commenting on the accuracy and effectiveness of GNNs in node classification or link prediction in academic 
contexts. For node classification, we will create a GNN model based on the vocabulary and neighbors as 
embeddings of each node, experimenting with different configurations to find the best model. Finally, 
we will take the results in terms of graph characteristics and model performance to analyze our dataset 
as an academic tool. In this regard, our technique is rather scalable, as these steps can be applied to 
academic datasets of nearly any field and in datasets beyond academic publications as well. However, 
this is also given the assumption that different academic fields follow similar citation networks to 
those listed, that these fields can be described by the vocabularies that they exhibit, and that 
these networks produce a graph that is compatible with neural network models. \par

\section{Experimental Setup and Results}

\subsection{Datasets}

Since the datasets Cora and Citeseer are included within some deep learning packages, 
we directly use those for constructing GNNs. Utilizing resources and configurations of 
included models within StellarGraph, Pytorch Geometric, and Keras, we can also construct 
predictive models for node classification and link prediction. \par

In creating our dataset, we query Web of Science for topics in machine learning 
hardware published between 1970 and 2022. For ease of use, we removed nodes without a 
DOI and duplicated values between categories so each node only belongs to one category. 
The collected data includes title, publishing year, abstract, and citations. \par

While Web of Science shows a close-to-linear growth of publications during this time, 
there has been an exponential growth of papers in machine learning hardware over the 
same period. We see a large spike in interest, following machine learning in general 
after OpenAI launched GPT. \par

With the text files generated, we constructed a NetworkX graph using DOI values to 
match paper citations. We also utilized the categories as labels, and the overall 
graph topography is in Figure A. This graph serves as our dataset once converted 
into StellarGraph or NetworkX Pytorch Geometric dataset instances as needed. \par

In total, our graph had 4951 nodes, though only 2605 nodes have non-zero edges. 
Looking at the in-degrees of each node, we see evidence of a scale-free network, 
where few nodes are popularly cited, but many are not referenced often. This may 
also be due to the recentness of these publications, as future papers will likely 
add on to those numbers. The number of paper citations is also indicative of its 
impact, with larger in-degrees meaning more outreach and influence. \par

Removing nodes without edges allows us to focus on the variety in edges and prevents 
the model from predicting 0 edges each time for high accuracy, the resulting is 
still disconnected, with an average degree of 5.0672, an average clustering coefficient 
of 0.1353, and a maximum diameter across all connected subgraphs of 16, 
with the average undirected path length being 4.6073 edges. \par

However, from observation, we notice that our graph is much smaller and less connected 
than the given datasets. As in Figure 1 below, there are lots of unconnected nodes. 
And, after removing non-zero edges, there are still plenty of nodes that have only 
one edge to another paper, likely due to their remaining citations not having an associated 
word vector. \par

To combat this, we increase the size of the WoS database, querying additional nodes from the 
WoS database. Then, we take the largest connected component of the 
larger graph to increase the overall connectivity of the graph. \par

\begin{figure}[htbp]
    \centerline{\includegraphics[scale=0.3] {wos_pic.png}}
    \caption{Large WoS network, Blue=ML Accelerators, Purple=Edge ML, Green=Neuromorphic Computing, Orange=Spiking Neural Network.}
    \label{fig}
\end{figure}

Before you begin to format your paper, first write and save the content as a 
separate text file. Complete all content and organizational editing before 
formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on 
proofreading, spelling and grammar.
